Manuscript Figures for Genome Biology

### 2018-05-28 manuscript_figures/manuscript_figures.Rmd
Decrease whitespace in Fig4; add A/B labels

pfdr <- plotMethodRanks(objs, 
                colLabels = c("sim", "sim"), 
                alpha = alpha, xlab = "Comparison",
                fill = "FDR",
                rowOrder = Fig4.rowOrder) +
          scale_fill_gradient2(high = scales::muted("red"), 
                         mid = "white", 
                         low = scales::muted("blue"), 
                         midpoint = alpha)

ptpr <- plotMethodRanks(objs, 
                colLabels = c("sim", "sim"), 
                alpha = alpha, xlab = "Comparison",
                fill = "TPR",
                colorLow = scales::muted("blue"), 
                colorHigh = "white",
                rowOrder = Fig4.rowOrder)

plot_grid(Fig4, pfdr + ylab("") + xlab(""), ptpr + ylab("") + xlab(""), 
          ncol=3, rel_widths = c(1,0.3,0.3))
ggsave(file.path(outdir, "Figure4.pdf"), width=12, height=5)

>>>>

pfdr <- plotMethodRanks(objs, 
                colLabels = c("sim", "sim"), 
                alpha = alpha, xlab = "Comparison",
                fill = "FDR",
                rowOrder = Fig4.rowOrder) +
          scale_fill_gradient2(high = "red", 
                         mid = "white", 
                         low = "blue", 
                         midpoint = alpha)

ptpr <- plotMethodRanks(objs, 
                colLabels = c("sim", "sim"), 
                alpha = alpha, xlab = "Comparison",
                fill = "TPR",
                colorLow = "blue", 
                colorHigh = "white",
                rowOrder = Fig4.rowOrder)

ggdraw() +
  draw_plot(pfdr + ylab("") + xlab(""), 0.57, 0, 0.22, 1) +
  draw_plot(ptpr + ylab("") + xlab(""), 0.78, 0, 0.22, 1) +
  draw_plot(Fig4, 0, 0, 0.60, 1) +
  draw_plot_label(c("A", "B"), c(0, 0.57), c(1, 1), size = 15)
ggsave(file.path(outdir, "Figure4.pdf"), width=12, height=5)
```
